### 2013-09-23 image_proc_methods.tex
more ultrasound segmentation details added

ARFI images were segmented using a similar procedure to the MR images.

>>>>

ARFI images were segmented using a similar procedure to the MR images.  B-mode
images were used to segment the prostate capsules since contrast between the
peripheral zone and the periprostatic fat can be low, and poor displacement SNR
can be present along the anterior aspect of the prostate in ARFI images, making
it difficult to delineate that boundary.  The central gland was segmented as a
stiffer region, relative to the peripheral zone, in the center of the prostate.
